\documentclass[12pt,letterpaper]{article}

\def\myauthor{Haksoo Choi}
\def\mytitle{haksoo-vita}
\def\myemail{haksoo@cs.ucla.edu}
\def\myname{haksoo}
\def\myweb{http://cs.ucla.edu/~haksoo}
\def\mylinkedin{http://www.linkedin.com/pub/haksoo-choi}
\def\mylinkedinpub{https://www.linkedin.com/pub/haksoo-choi/24/590/48}
\def\mykeywords{
  haksoo choi, 
  resume, 
  curriculum, 
  vita, 
  curriculum vita, 
  cv, 
  haksoo, 
  choi
}

\setlength\parindent{0pt}

\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{0pt}}%
{\end{itemize}}

\usepackage{url}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{ocgtools}
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=0.15in}
\usepackage[log-declarations=false]{xparse}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=1.125in,right=1in,left=2in]{geometry}
\usepackage[strict]{changepage}
\usepackage[
  ocgcolorlinks,
  urlcolor={[rgb]{0,0,0.54}},
  unicode,
  plainpages=false,
  pdfpagelabels,
  pdftitle={\mytitle},
  pdfauthor={\myauthor},
  pdfkeywords={\mykeywords}
]{hyperref}

\linespread{1.129}
\def\myvspace{\vspace{-0.22in}}

% fix ocgcolor link breaking; thanks due to Benjamin Lerner (http://goo.gl/VZKR7M)
\makeatletter
\AtBeginDocument{%
  \newlength{\temp@x}%
  \newlength{\temp@y}%
  \newlength{\temp@w}%
  \newlength{\temp@h}%
  \def\my@coords#1#2#3#4{%
    \setlength{\temp@x}{#1}%
    \setlength{\temp@y}{#2}%
    \setlength{\temp@w}{#3}%
    \setlength{\temp@h}{#4}%
    \adjustlengths{}%
    \my@pdfliteral{\strip@pt\temp@x\space\strip@pt\temp@y\space\strip@pt\temp@w\space\strip@pt\temp@h\space re}}%
  \ifpdf
    \typeout{In PDF mode}%
    \def\my@pdfliteral#1{\pdfliteral page{#1}}% I don't know why % this command...
    \def\adjustlengths{}%
  \fi
  \ifxetex
    \def\my@pdfliteral #1{\special{pdf: literal direct #1}}% isn't equivalent to this one
    \def\adjustlengths{\setlength{\temp@h}{-\temp@h}\addtolength{\temp@y}{1in}\addtolength{\temp@x}{-1in}}%
  \fi%
  \def\Hy@colorlink#1{%
    \begingroup
      \ifHy@ocgcolorlinks
        \def\Hy@ocgcolor{#1}%
        \my@pdfliteral{q}%
        \my@pdfliteral{7 Tr}% Set text mode to clipping-only
      \else
        \HyColor@UseColor#1%
      \fi
  }%
  \def\Hy@endcolorlink{%
    \ifHy@ocgcolorlinks%
      \my@pdfliteral{/OC/OCPrint BDC}%
      \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
      \my@pdfliteral{F}% Fill clipping path (the url's text) with current color
      \my@pdfliteral{EMC/OC/OCView BDC}%
      \begingroup%
        \expandafter\HyColor@UseColor\Hy@ocgcolor%
        \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
        \my@pdfliteral{F}% Fill clipping path (the url's text) with \Hy@ocgcolor
      \endgroup%
      \my@pdfliteral{EMC}%
      \my@pdfliteral{0 Tr}% Reset text to normal mode
      \my@pdfliteral{Q}%
    \fi
    \endgroup
  }%
}
\makeatother
% end fixes

\newcommand{\ML}{\textsc{Matlab}}
\newcommand{\Simu}{Simulink}
\newcommand{\MLS}{\ML{}/\Simu{}}
\newcommand{\apdl}{\textsc{APDL}}
\newcommand{\ansys}{\textsc{Ansys}}
\newcommand{\fluent}{\textsc{Fluent}}
\newcommand\CPP{C/C\ensuremath{+}\ensuremath{+}}
\newcommand{\Star}{\textsc{Star-CCM\ensuremath{+}}}

\newcommand{\mhead}[1]{\leavevmode\marginpar{\sffamily\footnotesize #1}}
\newcommand{\rdate}[1]{{\addfontfeature{Numbers=OldStyle} \hfill #1}}
\renewcommand{\date}[1]{{\addfontfeature{Numbers=OldStyle} #1}}
\renewcommand{\labelitemi}{-} 

\setmainfont[
  Ligatures={TeX,Common},
  BoldFont={AGaramondPro-Semibold},
]{Adobe Garamond Pro}
\setsansfont[
  Ligatures={TeX,Common},
  Letters=SmallCaps,
  Color=660000,
]{Adobe Garamond Pro}
\setmonofont{FontAwesome}

\begin{document}\flushbottom
\pagestyle{fancy} \setlength\headwidth{6.5in}
%\rhead{\textsc{paul d.~gessler—r\'{e}sum\'{e}—\thepage{} of \pageref*{LastPage}}} \cfoot{}
\rhead{\textsc{haksoo choi—cv—\thepage{} of \pageref*{LastPage}}} \cfoot{}
\thispagestyle{empty}
\begin{adjustwidth}{-1in}{}
{\Huge
  {\textsc{%
    {\addfontfeature{Style=TitlingCaps}H}\kern-1.5ptaksoo 
    %{\addfontfeature{Style=TitlingCaps}D}\kern-2pt.~%
    {\addfontfeature{Style=TitlingCaps}C}hoi}
  }
}
\hfill\hfill\hfill
{
  \begin{minipage}[b]{1.6in}
    %\flushleft \footnotesize 
    %2040 West Wisconsin Avenue \\ 
    %Apartment S406A \\ 
    %Milwaukee, WI~~53233-2098
  \end{minipage}
  \hfill
  \begin{minipage}[b]{2.5in}
    \flushright \footnotesize 
    %\href{tel:\myphone}{\myphone} \\ %\texttt{}~
    \href{mailto:\myemail}{\myemail} \\
    %\href{https://www.github.com/\myweb}{\texttt{}}~\href{\mylinkedin}{\texttt{}~\myweb}
    \href{\myweb}{http://cs.ucla.edu/\textasciitilde haksoo} \\
    \href{\mylinkedinpub}\mylinkedin \\
  \end{minipage}
}\par
\hrulefill
\end{adjustwidth}  
\reversemarginpar 
\setlength\marginparwidth{0.85in}
\medskip
\mhead{Summary}%
\myvspace
\begin{itemize}
\item Broad range of software research and development experience ranging from small-embedded to big-cloud systems, with deep understanding of underlying hardware, operating systems, and programming
languages.
\item Strong algorithmic and analytical thinking skills, with deep understanding of computer science.
\item An excellent problem solver, able to quickly understand complex problem space and figure out effective solutions and opportunities for improvements.
\item An effective team player, skilled in discussing ideas, communicating effectively, and cooperating with team members towards project and organizational goals.
\end{itemize}

\bigskip
\mhead{Education}%
\textbf{University of California, Los Angeles} \newline
\emph{Ph.D., Computer Science} (GPA: 3.97/4.0) \rdate{2009--2014} \newline
Thesis: Styles and the Design of Mobile-Cloud Sensing Software Architectures

\medskip
\textbf{Yonsei University, Seoul, Korea} \newline
\emph{M.Sc., Computer Science} (GPA: 4.27/4.3) \rdate{2007--2009} \newline
Thesis: Application-Specific Platform Builder for Deeply Embedded OS

\medskip
\textbf{University of California, Davis} \newline
\emph{Exchange Student, Computer Science} (GPA: 3.86/4.0, Major GPA: 3.91/4.0) \rdate{2006}

\medskip
\textbf{Yonsei University, Seoul, Korea} \newline
\emph{B.Sc., Computer Science} (GPA: 3.96/4.3, Major GPA: 4.3/4.3) \rdate{2000--2007}

\bigskip
\mhead{Experience}%
\textbf{University of California, Los Angeles} \rdate{\textsc{los angeles, ca}} \newline
\emph{Graduate Student Researcher, Networked Embedded Systems Lab.} \rdate{2009--2014}
\begin{itemize*}
  \item Architected and developed a distributed VM-based mobile-cloud system for privacy-aware sharing of personal sensor data.
  \item Developed algorithms and software for energy-efficient execution of machine-learning data-flows on heterogeneous multiple processor cores.
  \item Used Android native/app, Jersey, Restlet, Django, Informix DB Timeseries, MongoDB, MATLAB
\end{itemize*}

\bigskip
\textbf{Qualcomm} \rdate{\textsc{san diego, ca}} \newline
\emph{Intern, Coporate Research and Development} \rdate{06-09/2013, 06-09/2012}
\begin{itemize*}
  \item Designed a machine learning algorithm for inferring smartphone user’s motion status using cell tower   information. Project outcome became a part of U.S. Patent Application.
  \item Developed an Android NDK communication layer for Linux Wi-Fi WPS service and Android App for   facilitating Wi-Fi device association using QRCode. Project outcome demonstrated at CES 2013.
  \item Used Android native/app, MATLAB
\end{itemize*}

\bigskip
\textbf{IBM T.J. Watson Research Center} \rdate{\textsc{hawthorne, ny}} \newline
\emph{Intern, IT / Wireless Convergence Department} \rdate{01-04/2012}
\begin{itemize*}
  \item Designed a machine-learning algorithm for predicting ad-hoc Wi-Fi connectivity in vehicular network.  A part of software developed used in IBM production systems.
  \item Used QualNet, Weka.
\end{itemize*}

\bigskip
\textbf{Yonsei University} \rdate{\textsc{seoul, korea}} \newline
\emph{Graduate Student Researcher, Mobile Embedded System Lab.} \rdate{2005, 2007--2009}
\begin{itemize*}
  \item Designed a device driver framework and an application-specific kernel builder for a multi-threaded microcontroller operating system.
  \item Designed modifications of the SNMP protocol for low-power embedded IPv6 (6LoWPAN) networks.
  \item Designed IEEE 802.15.4-based MAC layer protocol for reliable/efficient transfer of large sensor data on low-rate wireless channel.
  \item Developed a strain-gauge sensor network system for structural health monitoring. 
  \item Used GNU Tools, firmware, embedded OS, TinyOS, MSP430, ATmega128
\end{itemize*}

\bigskip
\textbf{Samsung Electronics} \rdate{\textsc{seoul, korea}} \newline
\emph{Samsung S/W Membership, Robotic and Embedded Systems Lab.} \rdate{2005, 2007--2009}
\begin{itemize*}
  \item Developed a home networking module in intelligent modular service robot project.
  \item Designed TCP/IP communication architecture for multiple modules of the robot.
  \item Used embedded Linux, TCP/IP sockets, various sensors/actuators, TinyOS.
\end{itemize*}

\bigskip
\textbf{Korea Electronics Technology Institute} \rdate{\textsc{seoul, korea}} \newline
\emph{Intern, Intelligent IT System Research Center.} \rdate{2007--2008}
\begin{itemize*}
  \item Developed a surveillance human tracking system based on wireless passive infrared sensor networks.
  \item Designed mathematical abstraction of multiple indoor infrared sensors and algorithms for tracking human location.
  \item Used TinyOS, Windows MFC.
\end{itemize*}

\bigskip
\textbf{University of California, Davis} \rdate{\textsc{davis, ca}} \newline
\emph{Intern, Department of Biological and Agricultural Engineering} \rdate{06-10/2006}
\begin{itemize*}
  \item Developed an embedded software for localization of a harvesting truck.
  \item Designed algorithms for tracking a harvesting truck inside large tree field using various non-GPS sensors.
  \item Used embedded RTOS. Rabbit MCU, Dynamic C
\end{itemize*}

\bigskip
\mhead{Patents}%
Shankar Sadasivam, Haksoo Choi, Jin Won Lee, \emph{``Motion Classification Using a Combination of Low-Power Sensor Data and Modem Information,''} Qualcomm Technologies Inc., U.S. Patent Application \#14/479,167, 2014.

\bigskip
Sukwon Choi, Haksoo Choi, Sungchil Cho, Hojung Cha, \emph{``Structural Health Monitoring System,''} Yonsei University, Hybus Co. Ltd., Korea Patent \#10-0947042, 2010.

\bigskip
Hojung Cha, Haksoo Choi, Sukwon Choi, \emph{``Structural Health Monitoring Method,''} Yonsei University, Korea Patent \#10-0925801, 2009.

\bigskip
\mhead{Publications}%
%\textbf{In submission}\\
%TMC Journal
%
%Some Journal?
%
%\emph{``Measuring User Burden and Privacy Risks in Wearing and Sharing Mobile Sensors,''} Co-authored paper submitted to ACM Conference on Computer Human Interaction (CHI Notes), 2014.
%
%\bigskip
%\emph{``SensorAct: An IoT Middleware for Energy Management in Buildings,''} Co-authored paper submitted to IEEE Internet of Things Journal (IEEE-IoT), 2014.
%
%\bigskip
\textbf{Conferences}

\medskip
Chenguang Shen, Haksoo Choi, Supriyo Chakraborty, Mani Srivastava, \emph{``Towards a Rich Sensing Stack for IoT Devices,''} The 33rd IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Special Session, November 2014.

\bigskip
Chenguang Shen, Supriyo Chakraborty, Kasturi Rangan Raghavan, Haksoo Choi, Mani B Srivastava,\emph{``Exploiting Processor Heterogeneity for Energy Efficient Context Inference On Mobile Phones,''} The 5th USENIX Workshop on Power-Aware Computing and Systems (HotPower), November 2013.

\bigskip
Pandarasamy Arjunan, Nipun Batra, Haksoo Choi, Amarjeet Singh, Mani B Srivastava,\emph{``SensorAct: A Privacy and Security Aware Federated Middleware for Building Management,''} The 4th ACM Workshop On Embedded Systems for Energy-Efficiency In Buildings (BuildSys), November 2012.

\bigskip
Haksoo Choi, Raghu Ganti, Mudhakar Srivatsa, Ramya Raghavendra,\emph{``Content Dissemination Protocols in Hybrid Wireless Networks,''} The Annual Conference of U.S. Army Information Technology Agency (ACITA), September 2012.

\bigskip
Haksoo Choi, Supriyo Chakraborty, Mani B Srivastava,\emph{``Design and Evaluation of SensorSafe: a Framework for Achieving Behavioral Privacy in Sharing Personal Sensory Information,''} The 2nd IEEE International Symposium on Security and Privacy in Internet of Things (TrustCom-SPIoT), June 2012.

\bigskip
Haksoo Choi, Supriyo Chakraborty, Zainul M Charbiwala, Mani B Srivastava,\emph{``SensorSafe: a Framework for Privacy-Preserving Management of Personal Sensory Information,''} The 8th VLDB Workshop on Secure Data Management (VLDB-SDM), June 2011.

\bigskip
Supriyo Chakraborty, Haksoo Choi, Mani B Srivastava,\emph{``Demystifying Privacy In Sensory Data: A QoI based approach,''} The 3rd IEEE International Workshop on Information Quality and Quality of Service for Pervasive Computing (PerCom-IQ2S), March 2011.

\bigskip
Haksoo Choi, Nakyoung Kim, Hojung Cha,\emph{``6LoWPAN-SNMP: Simple Network Management Protocol for 6LoWPAN,''} The 11th IEEE International Conference on High Performance Computing and Communications (HPCC), June 2009.

\bigskip
Haksoo Choi, Sukwon Choi, Hojung Cha,\emph{``Structural Health Monitoring System based on Strain Gauge Enabled Wireless Sensor Nodes,''} The 5th IEEE International Conference on Networked Sensing Systems (INSS), June 2008.

\bigskip
Haksoo Choi, Chanmin Yoon, Hojung Cha,\emph{``Device Driver Abstraction for Multithreaded Sensor Network Operating Systems,''} The 5th European Conference on Wireless Sensor Networks (EWSN), February 2008.

\bigskip
Haksoo Choi, Byunghun Song, Hyung Su Lee,\emph{``Surveillance Tracking System Using Passive Infrared Motion Sensors in Wireless Sensor Networks,''} The 22nd IEEE International Conference on Information Networking (ICOIN), January 2008.

\bigskip
Ho Seok Ahn, In-Kyu Sa, Young Min Beak, Kwang Hee Lee, Haksoo Choi, Joong Kil Shin, Kyu Chul Kyung, Minhyuck Kim, Byung Soo Lim, Jin Young Choi,\emph{``Modular System Architecture of Intelligent Service Robots Focused on Smart Adapted Services,''} The 10th IEEE International Conference on Advanced Robotics (ICAR), August 2007.

\bigskip
\textbf{Journals}

\medskip
Supriyo Chakraborty, Zainul M Charbiwala, Haksoo Choi, Kasturi Rangan Raghavan, Mani B Srivastava,\emph{``Balancing Behavioral Privacy and Information Utility in Sensory Data Flows,''} The Journal of Pervasive and Mobile Computing, Elsevier, June 2012.

\bigskip
Uriel. A. Rosa, Todd S. Rosenstock, Haksoo Choi, David Pursell, Christopher J. Gliever, Patrick H. Brown, Shrini K. Upadhyaya,\emph{``Design and Evaluation of a Yield Monitoring System for Pistachios,''} Transaction of the American Society of Agricultural and Biological Engineers (ASABE), 2011.

\bigskip
\textbf{Posters and Demos}

\medskip
Haksoo Choi, Pandarasamy Arjunan, Mani B Srivastava, Amarjeet Singh, Supriyo Chakraborty, Chenguang Shen, Mahbubur Rahman,\emph{``Middleware for Pervasive Sensing and Actuation,''} UCLA Engineering Tech Forum, Poster Presentation, May 2013.

\bigskip
Pandarasamy Arjunan, Manaswi Saha, Manoj Gulati, Haksoo Choi, Nipun Batra, Amarjeet Singh, Mani B Srivastava, Pushpendra Singh,\emph{``SensorAct: Design and Implementation of Fine-grained Sensing and Control Sharing in Buildings,''} The 10th USENIX Symposium on Networked Systems Design and Implementation (NSDI), Poster Presentation, April 2013.

\bigskip
Haksoo Choi, Max E Greenblatt, Zainul M Charbiwala, Supriyo Chakraborty, Mani B. Srivastava,\emph{``SensorSafe: Privacy-Preserving Sharing of Sensory Information for Medical Studies and Healthcare,''} Center for Embedded Networked Sensing (CENS) 8th Annual Research Review, Poster Presentation, October 2010.

\bigskip
Yi Han, Kasturi Rangan Raghavan, Zainul Charbiwala, Haksoo Choi, Mani B. Srivastava,\emph{``Physiological Data Collection on Mobile Devices,''} Center for Embedded Networked Sensing (CENS) 8th Annual Research Review, Poster Presentation, October 2010.

\bigskip
Chanmin Yoon, Haksoo Choi, Seungwoo Lee, Hojung Cha, Byunghun Song, Hyungsu Lee,\emph{``Demo Abstract: IEEE 802.15.4a-Based Anchor-free Mobile Node Localization System,''} The 8th ACM/IEEE International Conference on Information Processing in Sensor Networks (IPSN), Demo Presentation, April 2009.

\bigskip
\textbf{Korean Conferences and Journals}

\medskip
Kwanghee Lee, Byunghun Song, Haksoo Choi,\emph{``Location Control Technique for Industrial Robots Based on RTLS,''} Korea Computer Congress (KCC), July 2008.

\bigskip
Sukwon Choi, Hyojung Shin, Chanmin Yoon, Haksoo Choi, Hojung Cha,\emph{``A Survey on Operating Systems for Wireless Sensor Networks,''} Communications of the Korea Information Science Society, December 2007.

\bigskip
Haksoo Choi, Kwanghee Lee, Taehyun Kim, Changkyun Lee, Ho Seok Ahn, Minwoo, Lee, Won Il Choi, Kyu Chul Kyung, Joongkil Shin, Minhyuck Kim,\emph{``Home Network System Based on Wireless Sensor Networks for Intelligent Service Robot,''} Korean Conference on Power Electronics, July 2007.

\bigskip
Kwanghee Lee, Kyu Chul Kyung, Haksoo Choi, Taehyun Kim, Changkyun Lee, Ho Seok Ahn, Minwoo Lee, Won Il Choi, Joongkil Shin, Minhyuck Kim,\emph{``Chair Robot System Using PSP,''} Korean Conference on Power Electronics, July 2007.

\bigskip
Changkyun Lee, WonIl Choi, Minwoo Lee, TaeHyun Kim, Ho Seok Ahn, JoongKil Shin, KwangHee Lee, KyuChul Kyung, Haksoo Choi, MinHyuck Kim,\emph{``Design of Intelligent Head Robot Using Rotating LED Array,''} Korean Conference on Power Electronics, July 2007.

\bigskip
\mhead{Teaching}%
Teaching Assistant, Embedded Systems, Graduate, University of California, Los Angeles, Summer 2011

\medskip
Teaching Assistant, Operating Systems, Undergraduate, Yonsei University, Seoul, Korea, Spring 2009.

\bigskip
\mhead{Talks}%
\emph{``SensorAct: A Privacy and Security Aware Federated Middleware for Building Management,''} The 4th ACM Workshop On Embedded Systems For Energy-Efficiency In Buildings (Buildsys), Toronto, Canada, November 2012.

\bigskip
\emph{``Design and Evaluation of SensorSafe: a Framework for Achieving Behavioral Privacy in Sharing Personal Sensory Information,''} The 2nd IEEE International Symposium on Security and Privacy in Internet of Things (TrustCom-SPIoT), Liverpool, UK, June 2012.

\bigskip
\emph{``SensorSafe: a Framework for Privacy-Preserving Management of Personal Sensory Information,''} The 8th VLDB Workshop on Secure Data Management (VLDB-SDM), Seattle, CA, September 2011.

\bigskip
\emph{``6LoWPAN-SNMP: Simple Network Management Protocol for 6LoWPAN,''} The 11th IEEE International Conference on High Performance Computing and Communications (HPCC), Korea, June 2009.

\bigskip
\emph{``Structural Health Monitoring System based on Strain Gauge Enabled Wireless Sensor Nodes,''} The 5th IEEE International Conference on Networked Sensing Systems (INSS), Kanazawa, Japan, June 2008.

\bigskip
\emph{``Location Control Techniques for Industrial Robots Based on RTLS,''} Korea Computer Congress 2008, Korea, June 2008.

\bigskip
\emph{``Device Driver Abstraction for Multithreaded Sensor Network Operating Systems,''} The 5th European Conference on Wireless Sensor Networks (EWSN), Bologna, Italy, February 2008.

\bigskip
\emph{``Surveillance Tracking System Using Passive Infrared Motion Sensors in Wireless Sensor Networks,''} The 22nd IEEE International Conference on Information Networking (ICOIN), Korea, January 2008.

\bigskip
\mhead{Awards}%
Best Paper Award, \emph{``6LoWPAN-SNMP: Simple Network Management Protocol for 6LoWPAN,''} The 11th IEEE International Conference on High Performance Computing and Communications, 2009.

\bigskip
Honorable Mention, \emph{``Mom’s Friend,''} IEEE RO-MAN International Robot Design Competition, 2007.

\bigskip
Gold Award for College, \emph{``Mom’s Friend,''} IEEE International Competition for Intelligent Robot Software, Ministry of Information and Communication / Korea University, 2007. 

\bigskip
First Prize, \emph{``Mom’s Friend,''} Intelligent Robot Competition, Kyungnam University, Korea, 2007.

\bigskip
Bronze Award, \emph{``Home Network System based on Wireless Sensor Networks,''} The 5th I.E. Competition, Korea Institute of Power Electronics, 2007.

\bigskip
Award for Excellence, \emph{``Structural Health Monitoring Using Wireless Sensor Nodes,''} Creativity Exhibition, College of Engineering, Yonsei University, Korea, 2007.

\bigskip
\mhead{Honors}%
High Honor Graduate, Yonsei University, 2007.

\medskip
Highest Honor Student, Yonsei University, 2001 / 2004 / 2005.

\bigskip
\mhead{Fellowships/ Scholarships}%
\myvspace
\begin{itemize*}
  \item Ph.D. Fellowship: Kwanjeong Educational Foundation (2009--2014)
  % \medskip
  \item Ph.D. Scholarship: Yonsei International Foundation (2011), Korea Foundation for Advanced Studies (2009)
  % \medskip
  \item M.Sc.~Scholarship: Brain Korea 21 Foundation (2007--2008), Yonsei University (2007)
  % \medskip
  \item B.Sc. Scholarship: Daum Communications Inc.~(2006), Joonha Hwang Foundation (2005), Yonsei University (2001)
\end{itemize*}

\bigskip
\mhead{Other\\ Experience}%
\emph{Computer Music}
\begin{itemize*}
  \item Developed a drum teaching software based on open-source MIDI program as a part of M.Sc.~course work.  Used Windows MFC, Win32 API, 2008.
\end{itemize*}

\medskip
\emph{Band / Leadership Experience}
\begin{itemize*}
  \item Medusa, Yonsei University, Korea, 2000-2002, 2004 / Director (2001): Promoted the club status from college level to semi-university by collaborating with the student club union.
  \item Forkcrane, a member of founders, Yonsei University, Korea, 2000--2002.
  \item Military Band, Republic of Korea Army, 2002--2004.
  \item MP22, a member of founders, Samsung S/W Membership, Korea, 2007.
  \item 11010, a member of founders, UCLA, 2011--2012 / Public concert at a live club, Empathy, Los Angeles, 06/2012.
\end{itemize*}

\bigskip
\mhead{Organizations}%
UCLA Korean Graduate Student Association, Staff Member \rdate{2010--2012}

\medskip
Republic of Korea Army, Discharged as a sergeant \rdate{2002--2004}

\end{document}

